(working title) Local Physiological Adaptation in \textit{Mimulus cardinalis}

### 2015-04-22 ms/ms.tex
Worked on manuscript Results

			Wet: daily/constant irrigation with cooled water
			Dry: start at week \#, gradually decrease watering frequency/level

@@

\subsubsection*{Growth and photosynthesis}

@@

  \hlcom{# Plot latitude versus PC1}
  \hlkwd{pdf}\hlstd{(}\hlkwd{paste}\hlstd{(pathFig,} \hlstr{"/Figure_PC1vLat.pdf"}\hlstd{,} \hlkwc{sep} \hlstd{=} \hlstr{""}\hlstd{),} \hlnum{5}\hlstd{,} \hlnum{5}\hlstd{)}
  \hlkwd{par}\hlstd{(}\hlkwc{mar} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{5}\hlstd{,} \hlnum{5}\hlstd{,} \hlnum{1}\hlstd{,} \hlnum{1}\hlstd{))}
  \hlkwd{plot}\hlstd{(focClim}\hlopt{$}\hlstd{Lat, focClim}\hlopt{$}\hlstd{PC1,} \hlkwc{xlim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{32}\hlstd{,} \hlnum{44}\hlstd{),} \hlkwc{ylim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlopt{-}\hlnum{4}\hlstd{,} \hlnum{4}\hlstd{),} \hlkwc{axes} \hlstd{= F,}
    \hlkwc{frame.plot} \hlstd{= T,} \hlkwc{type} \hlstd{=} \hlstr{"n"}\hlstd{,} \hlkwc{xlab} \hlstd{=} \hlstr{""}\hlstd{,} \hlkwc{ylab} \hlstd{=} \hlstr{""}\hlstd{)}
  \hlkwd{title}\hlstd{(}\hlkwc{xlab} \hlstd{=} \hlstr{"Latitude"}\hlstd{,} \hlkwc{cex.lab} \hlstd{=} \hlnum{1.5}\hlstd{)}
  \hlkwd{title}\hlstd{(}\hlkwc{ylab} \hlstd{=} \hlkwd{substitute}\hlstd{(}\hlkwd{plain}\hlstd{(Principal}\hlopt{~}\hlstd{Component}\hlopt{~}\hlnum{1}\hlstd{)}\hlopt{~}\hlkwd{group}\hlstd{(}\hlstr{"("}\hlstd{, x,} \hlstr{")"}\hlstd{),}
    \hlkwd{list}\hlstd{(}\hlkwc{x} \hlstd{= pve)))}
  \hlkwd{axis}\hlstd{(}\hlnum{1}\hlstd{,} \hlkwc{at} \hlstd{=} \hlkwd{seq}\hlstd{(}\hlnum{32}\hlstd{,} \hlnum{44}\hlstd{,} \hlnum{4}\hlstd{),} \hlkwc{labels} \hlstd{=} \hlkwd{c}\hlstd{(}\hlkwd{expression}\hlstd{(}\hlnum{32}\hlopt{*}\hlstd{degree),} \hlkwd{expression}\hlstd{(}\hlnum{36}\hlopt{*}\hlstd{degree),}
    \hlkwd{expression}\hlstd{(}\hlnum{40}\hlopt{*}\hlstd{degree),} \hlkwd{expression}\hlstd{(}\hlnum{44}\hlopt{*}\hlstd{degree)),} \hlkwc{lwd} \hlstd{=} \hlnum{0}\hlstd{,} \hlkwc{lwd.ticks} \hlstd{=} \hlnum{1}\hlstd{)}
  \hlkwd{axis}\hlstd{(}\hlnum{2}\hlstd{,} \hlkwc{at} \hlstd{=} \hlkwd{seq}\hlstd{(}\hlopt{-}\hlnum{4}\hlstd{,} \hlnum{4}\hlstd{,} \hlnum{2}\hlstd{),} \hlkwc{las} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{lwd} \hlstd{=} \hlnum{0}\hlstd{,} \hlkwc{lwd.ticks} \hlstd{=} \hlnum{1}\hlstd{)}
  \hlstd{fitLat} \hlkwb{<-} \hlkwd{lm}\hlstd{(PC1} \hlopt{~} \hlstd{Latitude,} \hlkwc{data} \hlstd{= focClim)}

@@

\begin{table}[ht]
   \centering
   \topcaption{Population, treatment effects}
   \begin{tabular}{@{} llllllll @{}}
      \toprule
                                   & Germination & Leaf expansion & Stem elongation & Photosynthesis & Intrin. Photo & Mortality \\
                                   & survreg     & lmer           & lmer            & lmer           & lmer          & glm \\
      \midrule
  Population                       &
    ***  &
    *** &
    *** &
    *** & 
    *** & 
    *** & \\
  Temperature                      &
    NA                                                          &
    ***    &
    *** &
    *** & 
     &     *** & \\
  Water                            &
    NA                                                          &
    ***   &
    ***   &
    *** & 
     &     
    *** & \\
  Pop $\times$ Temp                &
    NA                                                          &
     &
     &
    * & 
     &     
    * & \\
  Pop $\times$ Water               &
     NA                                                          &
    * &
     &
     & 
     &     
     & \\
  Temp $\times$ Water              &
    NA                                                          &
     &
    *** &
     & 
     &     
    *** & \\
  Pop $\times$ Temp $\times$ Water &
    NA                                                          &
     &
     &
     & 
     &     
     & \\
      \bottomrule
   \end{tabular}
\end{table}

@@

\subsection*{Little evidence population by treatment interactions}

>>>>

      April 14 germinate
      Before May 20 (36 days): 7.5 min (complete flood) every 2 hours
      between May 20 to June 10 (57 days), down to 30 seconds, 1x per day
			Wet: daily/constant irrigation with cooled water
			Dry: start at week \#, gradually decrease watering frequency/level

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{library}\hlstd{(scales)} \hlcom{# for color transparency}
\hlstd{exptlDes} \hlkwb{<-} \hlkwd{read.csv}\hlstd{(}\hlkwd{paste}\hlstd{(pathDat,} \hlstr{"/ExperimentalDesign.csv"}\hlstd{,} \hlkwc{sep} \hlstd{=} \hlstr{""}\hlstd{))}

\hlkwd{pdf}\hlstd{(}\hlkwd{paste}\hlstd{(pathFig,} \hlstr{"/ExperimentalDesignBase.pdf"}\hlstd{,} \hlkwc{sep} \hlstd{=} \hlstr{""}\hlstd{),} \hlnum{7}\hlstd{,} \hlnum{5}\hlstd{)}
\hlkwd{par}\hlstd{(}\hlkwc{mai} \hlstd{=} \hlkwd{rep}\hlstd{(}\hlnum{1}\hlstd{,} \hlnum{4}\hlstd{))}
\hlkwd{plot}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{0}\hlstd{,} \hlkwc{type} \hlstd{=} \hlstr{"n"}\hlstd{,} \hlkwc{xlim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{0}\hlstd{,} \hlkwd{max}\hlstd{(exptlDes}\hlopt{$}\hlstd{DayN)),} \hlkwc{ylim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlopt{-}\hlnum{1}\hlstd{,} \hlnum{41}\hlstd{),}
                 \hlkwc{axes} \hlstd{= F,} \hlkwc{frame.plot} \hlstd{= T,} \hlkwc{cex.lab} \hlstd{=} \hlnum{1.5}\hlstd{,} \hlkwc{xlab} \hlstd{=} \hlstr{"Key treatments and measurements"}\hlstd{,}
     \hlkwc{ylab} \hlstd{=} \hlkwd{expression}\hlstd{(}\hlkwd{paste}\hlstd{(}\hlstr{"Temperature ("}\hlstd{,} \hlkwd{phantom}\hlstd{()}\hlopt{*}\hlstd{degree,} \hlstr{"C)"}\hlstd{)))}

\hlcom{# Temperature axis}
\hlkwd{axis}\hlstd{(}\hlnum{2}\hlstd{,} \hlkwc{at} \hlstd{=} \hlkwd{seq}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{40}\hlstd{,} \hlnum{10}\hlstd{),} \hlkwc{lwd} \hlstd{=} \hlnum{0}\hlstd{,} \hlkwc{lwd.ticks} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{las} \hlstd{=} \hlnum{1}\hlstd{,}
        \hlkwc{labels} \hlstd{=} \hlkwd{c}\hlstd{(}\hlkwd{expression}\hlstd{(}\hlnum{0}\hlopt{*}\hlstd{degree),} \hlkwd{expression}\hlstd{(}\hlnum{10}\hlopt{*}\hlstd{degree),} \hlkwd{expression}\hlstd{(}\hlnum{20}\hlopt{*}\hlstd{degree),}
                                                 \hlkwd{expression}\hlstd{(}\hlnum{30}\hlopt{*}\hlstd{degree),} \hlkwd{expression}\hlstd{(}\hlnum{40}\hlopt{*}\hlstd{degree)))}
\hlcom{# Axis of time on top}
\hlkwd{mtext}\hlstd{(}\hlstr{"Days after sowing"}\hlstd{,} \hlkwc{side} \hlstd{=} \hlnum{3}\hlstd{,} \hlkwc{line} \hlstd{=} \hlnum{3.5}\hlstd{,} \hlkwc{cex} \hlstd{=} \hlnum{1.5}\hlstd{)}
\hlkwd{mtext}\hlstd{(}\hlstr{"(Date for climate simulation)"}\hlstd{,} \hlkwc{side} \hlstd{=} \hlnum{3}\hlstd{,} \hlkwc{line} \hlstd{=} \hlnum{2.25}\hlstd{,} \hlkwc{cex} \hlstd{=} \hlnum{1.5}\hlstd{)}
\hlkwd{axis}\hlstd{(}\hlnum{3}\hlstd{,} \hlkwc{at} \hlstd{=} \hlkwd{seq}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{90}\hlstd{,} \hlnum{30}\hlstd{),} \hlkwc{lwd} \hlstd{=} \hlnum{0}\hlstd{,} \hlkwc{lwd.ticks} \hlstd{=} \hlnum{1}\hlstd{)}
\hlkwd{axis}\hlstd{(}\hlnum{3}\hlstd{,} \hlkwc{at} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{17}\hlstd{,} \hlnum{47}\hlstd{,} \hlnum{78}\hlstd{),} \hlkwc{lwd} \hlstd{=} \hlnum{0}\hlstd{,} \hlkwc{lwd.ticks} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{line} \hlstd{=} \hlopt{-}\hlnum{0.5}\hlstd{,}
     \hlkwc{labels} \hlstd{=} \hlkwd{c}\hlstd{(}\hlstr{"(June)"}\hlstd{,} \hlstr{"(July)"}\hlstd{,} \hlstr{"(August)"}\hlstd{))}

\hlcom{# Indicate sowing, beginning of temperature and drought treatments}
\hlkwd{abline}\hlstd{(}\hlkwc{v} \hlstd{=} \hlnum{0}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"grey"}\hlstd{,} \hlkwc{lwd} \hlstd{=} \hlnum{2}\hlstd{,} \hlkwc{lty} \hlstd{=} \hlnum{2}\hlstd{)}
\hlkwd{mtext}\hlstd{(}\hlstr{"Sow"}\hlstd{,} \hlkwc{side} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{at} \hlstd{=} \hlnum{0}\hlstd{,} \hlkwc{line} \hlstd{=} \hlnum{0}\hlstd{)}
\hlkwd{abline}\hlstd{(}\hlkwc{v} \hlstd{=} \hlnum{17}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"grey"}\hlstd{,} \hlkwc{lwd} \hlstd{=} \hlnum{2}\hlstd{,} \hlkwc{lty} \hlstd{=} \hlnum{2}\hlstd{)}
\hlkwd{mtext}\hlstd{(}\hlstr{"Temp\textbackslash{}nTreatment"}\hlstd{,} \hlkwc{side} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{at} \hlstd{=} \hlnum{17}\hlstd{,} \hlkwc{line} \hlstd{=} \hlnum{1}\hlstd{)}
\hlkwd{abline}\hlstd{(}\hlkwc{v} \hlstd{=} \hlnum{37}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"grey"}\hlstd{,} \hlkwc{lwd} \hlstd{=} \hlnum{2}\hlstd{,} \hlkwc{lty} \hlstd{=} \hlnum{2}\hlstd{)}
\hlkwd{mtext}\hlstd{(}\hlstr{"Drought\textbackslash{}nTreatment"}\hlstd{,} \hlkwc{side} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{at} \hlstd{=} \hlnum{37}\hlstd{,} \hlkwc{line} \hlstd{=} \hlnum{1}\hlstd{)}

\hlcom{# Polygon of Hot treatment, min and max}
\hlkwd{with}\hlstd{(exptlDes[}\hlnum{18}\hlopt{:}\hlnum{94}\hlstd{, ],} \hlkwd{polygon}\hlstd{(}\hlkwd{c}\hlstd{(}\hlnum{17}\hlopt{:}\hlnum{93}\hlstd{,} \hlnum{93}\hlopt{:}\hlnum{17}\hlstd{),} \hlkwd{c}\hlstd{(Tmin_hot,} \hlkwd{rev}\hlstd{(Tmax_hot)),}
  \hlkwc{border} \hlstd{=} \hlnum{NA}\hlstd{,} \hlkwc{col} \hlstd{=} \hlkwd{alpha}\hlstd{(primShade0,} \hlnum{0.25}\hlstd{)))}

\hlcom{# Polygon of Cool treatment, min and max}
\hlkwd{with}\hlstd{(exptlDes[}\hlnum{18}\hlopt{:}\hlnum{94}\hlstd{, ],} \hlkwd{polygon}\hlstd{(}\hlkwd{c}\hlstd{(}\hlnum{17}\hlopt{:}\hlnum{93}\hlstd{,} \hlnum{93}\hlopt{:}\hlnum{17}\hlstd{),} \hlkwd{c}\hlstd{(Tmin_cool,} \hlkwd{rev}\hlstd{(Tmax_cool)),}
  \hlkwc{border} \hlstd{=} \hlnum{NA}\hlstd{,} \hlkwc{col} \hlstd{=} \hlkwd{alpha}\hlstd{(sec1shade0,} \hlnum{0.25}\hlstd{)))}

\hlcom{# Lines with average temperature}
\hlkwd{with}\hlstd{(exptlDes[}\hlnum{18}\hlopt{:}\hlnum{94}\hlstd{, ],} \hlkwd{points}\hlstd{(}\hlnum{17}\hlopt{:}\hlnum{93}\hlstd{, Tavg_hot,} \hlkwc{lwd} \hlstd{=} \hlnum{2}\hlstd{,} \hlkwc{type} \hlstd{=} \hlstr{"l"}\hlstd{,}
        \hlkwc{col} \hlstd{= primShade3))}
\hlkwd{with}\hlstd{(exptlDes[}\hlnum{18}\hlopt{:}\hlnum{94}\hlstd{, ],} \hlkwd{points}\hlstd{(}\hlnum{17}\hlopt{:}\hlnum{93}\hlstd{, Tavg_cool,} \hlkwc{lwd} \hlstd{=} \hlnum{2}\hlstd{,} \hlkwc{type} \hlstd{=} \hlstr{"l"}\hlstd{,}
        \hlkwc{col} \hlstd{= sec1shade3))}

\hlcom{# Rug indicating measurment timing}
\hlkwd{rect}\hlstd{(}\hlnum{6}\hlstd{,} \hlopt{-}\hlnum{2}\hlstd{,} \hlnum{17}\hlstd{,} \hlnum{0}\hlstd{,} \hlkwc{border} \hlstd{=} \hlstr{"white"}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"grey"}\hlstd{)}
\hlkwd{with}\hlstd{(exptlDes,} \hlkwd{text}\hlstd{(}\hlnum{11.5}\hlstd{,} \hlopt{-}\hlnum{1}\hlstd{,} \hlkwc{labels} \hlstd{=} \hlstr{"Germ"}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"white"}\hlstd{,} \hlkwc{font} \hlstd{=} \hlnum{3}\hlstd{,}
  \hlkwc{cex} \hlstd{=} \hlnum{0.9}\hlstd{))}

\hlkwd{with}\hlstd{(exptlDes,} \hlkwd{rect}\hlstd{(}\hlkwd{min}\hlstd{(}\hlkwd{which}\hlstd{(LERmeas)),} \hlopt{-}\hlnum{2}\hlstd{,} \hlkwd{max}\hlstd{(}\hlkwd{which}\hlstd{(LERmeas)),} \hlnum{0}\hlstd{,}
        \hlkwc{border} \hlstd{=} \hlstr{"white"}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"grey"}\hlstd{))}
\hlkwd{with}\hlstd{(exptlDes,} \hlkwd{text}\hlstd{(}\hlkwd{min}\hlstd{((}\hlkwd{which}\hlstd{(LERmeas))} \hlopt{+} \hlkwd{max}\hlstd{(}\hlkwd{which}\hlstd{(LERmeas)))} \hlopt{/} \hlnum{2}\hlstd{,} \hlopt{-}\hlnum{1}\hlstd{,}
        \hlkwc{labels} \hlstd{=} \hlstr{"LER"}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"white"}\hlstd{,} \hlkwc{font} \hlstd{=} \hlnum{3}\hlstd{,} \hlkwc{cex} \hlstd{=} \hlnum{0.9}\hlstd{))}

\hlkwd{with}\hlstd{(exptlDes,} \hlkwd{rect}\hlstd{(}\hlkwd{min}\hlstd{(}\hlkwd{which}\hlstd{(SERmeas)),} \hlnum{0}\hlstd{,} \hlkwd{max}\hlstd{(}\hlkwd{which}\hlstd{(SERmeas)),} \hlnum{2}\hlstd{,}
        \hlkwc{border} \hlstd{=} \hlstr{"white"}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"grey"}\hlstd{))}
\hlkwd{with}\hlstd{(exptlDes,} \hlkwd{text}\hlstd{(}\hlkwd{min}\hlstd{((}\hlkwd{which}\hlstd{(SERmeas))} \hlopt{+} \hlkwd{max}\hlstd{(}\hlkwd{which}\hlstd{(SERmeas)))} \hlopt{/} \hlnum{2}\hlstd{,} \hlnum{1}\hlstd{,}
        \hlkwc{labels} \hlstd{=} \hlstr{"SER"}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"white"}\hlstd{,} \hlkwc{font} \hlstd{=} \hlnum{3}\hlstd{,} \hlkwc{cex} \hlstd{=} \hlnum{0.9}\hlstd{))}

\hlkwd{with}\hlstd{(exptlDes,} \hlkwd{rect}\hlstd{(}\hlkwd{min}\hlstd{(}\hlkwd{which}\hlstd{(Harvest)),} \hlopt{-}\hlnum{2}\hlstd{,} \hlkwd{max}\hlstd{(}\hlkwd{which}\hlstd{(Harvest)),} \hlnum{0}\hlstd{,}
        \hlkwc{border} \hlstd{=} \hlstr{"white"}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"grey"}\hlstd{))}
\hlkwd{with}\hlstd{(exptlDes,} \hlkwd{text}\hlstd{(}\hlkwd{min}\hlstd{((}\hlkwd{which}\hlstd{(Harvest))} \hlopt{+} \hlkwd{max}\hlstd{(}\hlkwd{which}\hlstd{(Harvest)))} \hlopt{/} \hlnum{2}\hlstd{,} \hlopt{-}\hlnum{1}\hlstd{,}
        \hlkwc{labels} \hlstd{=} \hlstr{"Harvest"}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"white"}\hlstd{,} \hlkwc{font} \hlstd{=} \hlnum{3}\hlstd{,} \hlkwc{cex} \hlstd{=} \hlnum{0.9}\hlstd{))}

\hlkwd{with}\hlstd{(exptlDes,} \hlkwd{text}\hlstd{(}\hlkwd{min}\hlstd{((}\hlkwd{which}\hlstd{(PhotoMeas))} \hlopt{+} \hlkwd{max}\hlstd{(}\hlkwd{which}\hlstd{(PhotoMeas)))} \hlopt{/} \hlnum{2}\hlstd{,} \hlnum{5}\hlstd{,}
        \hlkwc{labels} \hlstd{=} \hlstr{"Photo"}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"grey"}\hlstd{,} \hlkwc{font} \hlstd{=} \hlnum{3}\hlstd{,} \hlkwc{cex} \hlstd{=} \hlnum{0.9}\hlstd{))}
\hlkwd{with}\hlstd{(exptlDes,} \hlkwd{rect}\hlstd{(}\hlkwd{min}\hlstd{(}\hlkwd{which}\hlstd{(PhotoMeas)),} \hlnum{2}\hlstd{,} \hlkwd{max}\hlstd{(}\hlkwd{which}\hlstd{(PhotoMeas)),} \hlnum{4}\hlstd{,}
        \hlkwc{border} \hlstd{=} \hlstr{"white"}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"grey"}\hlstd{))}
\hlcom{#with(exptlDes, text(min((which(PhotoMeas)) + max(which(PhotoMeas))) / 2, 3, }
\hlcom{#	labels = "Photo", col = "white", font = 3, cex = 0.9))}

\hlkwd{dev.off}\hlstd{()}
\end{alltt}
\begin{verbatim}
## pdf 
##   2
\end{verbatim}
\begin{alltt}
\hlcom{# Legend}
\hlkwd{pdf}\hlstd{(}\hlkwd{paste}\hlstd{(pathFig,} \hlstr{"/ExperimentalDesignLegend.pdf"}\hlstd{,} \hlkwc{sep} \hlstd{=} \hlstr{""}\hlstd{),} \hlnum{1.5}\hlstd{,} \hlnum{2}\hlstd{)}
\hlkwd{par}\hlstd{(}\hlkwc{mai} \hlstd{=} \hlkwd{rep}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{4}\hlstd{))}
\hlkwd{plot}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{0}\hlstd{,} \hlkwc{type} \hlstd{=} \hlstr{"n"}\hlstd{,} \hlkwc{xlim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{1.5}\hlstd{),} \hlkwc{ylim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{1}\hlstd{),} \hlkwc{axes} \hlstd{= F)}

\hlkwd{polygon}\hlstd{(}\hlkwd{c}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{0.5}\hlstd{,} \hlnum{1}\hlstd{,} \hlnum{1}\hlstd{,} \hlnum{0.5}\hlstd{,} \hlnum{0}\hlstd{),} \hlkwd{c}\hlstd{(}\hlnum{0.8}\hlstd{,} \hlnum{1}\hlstd{,} \hlnum{1}\hlstd{,} \hlnum{0.55}\hlstd{,} \hlnum{0.55}\hlstd{,} \hlnum{0.35}\hlstd{),} \hlkwc{border} \hlstd{=} \hlnum{NA}\hlstd{,}
                                \hlkwc{col} \hlstd{=} \hlkwd{alpha}\hlstd{(primShade0,} \hlnum{0.25}\hlstd{))}
\hlkwd{polygon}\hlstd{(}\hlkwd{c}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{0.5}\hlstd{,} \hlnum{1}\hlstd{,} \hlnum{1}\hlstd{,} \hlnum{0.5}\hlstd{,} \hlnum{0}\hlstd{),} \hlkwd{c}\hlstd{(}\hlnum{0.6}\hlstd{,} \hlnum{0.45}\hlstd{,} \hlnum{0.45}\hlstd{,} \hlnum{0}\hlstd{,} \hlnum{0}\hlstd{,} \hlnum{0.15}\hlstd{),} \hlkwc{border} \hlstd{=} \hlnum{NA}\hlstd{,}
                                \hlkwc{col} \hlstd{=} \hlkwd{alpha}\hlstd{(sec1shade0,} \hlnum{0.25}\hlstd{))}
\hlkwd{points}\hlstd{(}\hlkwd{c}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{0.5}\hlstd{,} \hlnum{1}\hlstd{),} \hlkwd{c}\hlstd{(}\hlnum{0.575}\hlstd{,} \hlnum{0.775}\hlstd{,} \hlnum{0.775}\hlstd{),} \hlkwc{lwd} \hlstd{=} \hlnum{2}\hlstd{,} \hlkwc{type} \hlstd{=} \hlstr{"l"}\hlstd{,} \hlkwc{col} \hlstd{= primShade3)}
\hlkwd{points}\hlstd{(}\hlkwd{c}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{0.5}\hlstd{,} \hlnum{1}\hlstd{),} \hlkwd{c}\hlstd{(}\hlnum{0.375}\hlstd{,} \hlnum{0.225}\hlstd{,} \hlnum{0.225}\hlstd{),} \hlkwc{lwd} \hlstd{=} \hlnum{2}\hlstd{,} \hlkwc{type} \hlstd{=} \hlstr{"l"}\hlstd{,} \hlkwc{col} \hlstd{= sec1shade3)}
\hlkwd{text}\hlstd{(}\hlnum{0.5}\hlstd{,} \hlnum{0.9}\hlstd{,} \hlkwc{labels} \hlstd{=} \hlstr{"Hot"}\hlstd{,} \hlkwc{col} \hlstd{= primShade3)}
\hlkwd{text}\hlstd{(}\hlnum{0.5}\hlstd{,} \hlnum{0.1}\hlstd{,} \hlkwc{labels} \hlstd{=} \hlstr{"Cool"}\hlstd{,} \hlkwc{col} \hlstd{= sec1shade3)}
\hlkwd{text}\hlstd{(}\hlnum{1.25}\hlstd{,} \hlnum{1}\hlstd{,} \hlkwc{labels} \hlstd{=} \hlstr{"Max"}\hlstd{,} \hlkwc{col} \hlstd{=} \hlkwd{alpha}\hlstd{(primShade0,} \hlnum{0.25}\hlstd{))}
\hlkwd{text}\hlstd{(}\hlnum{1.25}\hlstd{,} \hlnum{0.55}\hlstd{,} \hlkwc{labels} \hlstd{=} \hlstr{"Min"}\hlstd{,} \hlkwc{col} \hlstd{=} \hlkwd{alpha}\hlstd{(primShade0,} \hlnum{0.25}\hlstd{))}
\hlkwd{text}\hlstd{(}\hlnum{1.25}\hlstd{,} \hlnum{0.775}\hlstd{,} \hlkwc{labels} \hlstd{=} \hlstr{"Mean"}\hlstd{,} \hlkwc{col} \hlstd{= primShade3)}

\hlkwd{text}\hlstd{(}\hlnum{1.25}\hlstd{,} \hlnum{0}\hlstd{,} \hlkwc{labels} \hlstd{=} \hlstr{"Min"}\hlstd{,} \hlkwc{col} \hlstd{=} \hlkwd{alpha}\hlstd{(sec1shade0,} \hlnum{0.25}\hlstd{))}
\hlkwd{text}\hlstd{(}\hlnum{1.25}\hlstd{,} \hlnum{0.45}\hlstd{,} \hlkwc{labels} \hlstd{=} \hlstr{"Max"}\hlstd{,} \hlkwc{col} \hlstd{=} \hlkwd{alpha}\hlstd{(sec1shade0,} \hlnum{0.25}\hlstd{))}
\hlkwd{text}\hlstd{(}\hlnum{1.25}\hlstd{,} \hlnum{0.225}\hlstd{,} \hlkwc{labels} \hlstd{=} \hlstr{"Mean"}\hlstd{,} \hlkwc{col} \hlstd{= sec1shade3)}

\hlkwd{dev.off}\hlstd{()}
\end{alltt}
\begin{verbatim}
## pdf 
##   2
\end{verbatim}
\end{kframe}
\end{knitrout}

\begin{figure}[h!]
	\centerline{\includegraphics[width=1\textwidth]{Figures/Figure_ExptlDes.pdf}}
	\usefont{T1}{phv}{m}{n}
	\fontsize{10}{12}
	\selectfont
	\caption[Experimental Design]{CAPTION}
	\label{fig:Fig_ExptlDes}
\end{figure}

\subsection*{Measurements: Growth and photosynthesis}

@@

  \hlcom{# Plot latitude versus PC1}
  \hlkwd{pdf}\hlstd{(}\hlkwd{paste}\hlstd{(pathFig,} \hlstr{"/Figure_PC1vLat.pdf"}\hlstd{,} \hlkwc{sep} \hlstd{=} \hlstr{""}\hlstd{),} \hlnum{5.5}\hlstd{,} \hlnum{5}\hlstd{)}
  \hlkwd{par}\hlstd{(}\hlkwc{mai} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{1}\hlstd{,} \hlnum{1.5}\hlstd{,} \hlnum{0.25}\hlstd{,} \hlnum{0.25}\hlstd{))}
  \hlkwd{plot}\hlstd{(focClim}\hlopt{$}\hlstd{Lat, focClim}\hlopt{$}\hlstd{PC1,} \hlkwc{xlim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{32}\hlstd{,} \hlnum{44}\hlstd{),} \hlkwc{ylim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlopt{-}\hlnum{4}\hlstd{,} \hlnum{4}\hlstd{),} \hlkwc{axes} \hlstd{= F,}
    \hlkwc{frame.plot} \hlstd{= T,} \hlkwc{type} \hlstd{=} \hlstr{"n"}\hlstd{,} \hlkwc{xlab} \hlstd{=} \hlstr{""}\hlstd{,} \hlkwc{ylab} \hlstd{=} \hlstr{""}\hlstd{)}
  \hlkwd{title}\hlstd{(}\hlkwc{xlab} \hlstd{=} \hlstr{"Latitude"}\hlstd{,} \hlkwc{cex.lab} \hlstd{=} \hlnum{1.5}\hlstd{)}
  \hlkwd{title}\hlstd{(}\hlkwc{ylab} \hlstd{=} \hlkwd{substitute}\hlstd{(}\hlkwd{plain}\hlstd{(Principal}\hlopt{~}\hlstd{Component}\hlopt{~}\hlnum{1}\hlstd{)}\hlopt{~}\hlkwd{group}\hlstd{(}\hlstr{"("}\hlstd{, x,} \hlstr{")"}\hlstd{),}
    \hlkwd{list}\hlstd{(}\hlkwc{x} \hlstd{= pve)))}
  \hlkwd{axis}\hlstd{(}\hlnum{1}\hlstd{,} \hlkwc{at} \hlstd{=} \hlkwd{seq}\hlstd{(}\hlnum{32}\hlstd{,} \hlnum{44}\hlstd{,} \hlnum{4}\hlstd{),} \hlkwc{labels} \hlstd{=} \hlkwd{c}\hlstd{(}\hlkwd{expression}\hlstd{(}\hlnum{32}\hlopt{*}\hlstd{degree),}
                \hlkwd{expression}\hlstd{(}\hlnum{36}\hlopt{*}\hlstd{degree),} \hlkwd{expression}\hlstd{(}\hlnum{40}\hlopt{*}\hlstd{degree),} \hlkwd{expression}\hlstd{(}\hlnum{44}\hlopt{*}\hlstd{degree)),}
                \hlkwc{lwd} \hlstd{=} \hlnum{0}\hlstd{,} \hlkwc{lwd.ticks} \hlstd{=} \hlnum{1}\hlstd{)}
  \hlkwd{axis}\hlstd{(}\hlnum{2}\hlstd{,} \hlkwc{at} \hlstd{=} \hlkwd{seq}\hlstd{(}\hlopt{-}\hlnum{4}\hlstd{,} \hlnum{4}\hlstd{,} \hlnum{2}\hlstd{),} \hlkwc{las} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{lwd} \hlstd{=} \hlnum{0}\hlstd{,} \hlkwc{lwd.ticks} \hlstd{=} \hlnum{1}\hlstd{)}
  \hlstd{fitLat} \hlkwb{<-} \hlkwd{lm}\hlstd{(PC1} \hlopt{~} \hlstd{Latitude,} \hlkwc{data} \hlstd{= focClim)}

        \hlcom{# Label y-axis from slow to fast growth}
        \hlkwd{mtext}\hlstd{(}\hlkwd{c}\hlstd{(}\hlstr{"Slow\textbackslash{}nGrowth"}\hlstd{,} \hlstr{"Fast\textbackslash{}nGrowth"}\hlstd{),} \hlnum{2}\hlstd{,} \hlkwc{at} \hlstd{=} \hlkwd{c}\hlstd{(}\hlopt{-}\hlnum{4}\hlstd{,} \hlnum{4}\hlstd{),} \hlkwc{cex} \hlstd{=} \hlnum{1.25}\hlstd{,}
                                \hlkwc{font} \hlstd{=} \hlnum{3}\hlstd{,} \hlkwc{las} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{line} \hlstd{=} \hlnum{4}\hlstd{,} \hlkwc{adj} \hlstd{=} \hlnum{0.5}\hlstd{)}

@@

@@

Genetic differences between populations affecting originsmal function and performance point to traits that may be involved in local adaptation. Using a common garden design, we identified strong genetic differences in germination, growth, and photosynthetic rate among populations of \textit{M. cardinalis} (Table~\ref{Table_AnovaSummary}). A single principal component captured 74.2 %\% of among population trait variation, defining an axis of variation from fast to slow growth (Fig~\ref{Fig_PC1vLat}). As we explain below, intrinsic differences between populations in terms of plant function (photosynthesis) and performance (growth) contrasted greatly with little variation in plasticity.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Table of Population, Treatment, Population x Treatment interactions for varies traits
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
